Schramm-Loewner evolution in tricritical Ising model

### 2013-06-14 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Some Mathematica code added

The weight of the spin configuration $C$ is equal to the product of
face weights and boundary weights:
\begin{equation}
  \label{eq:7}
  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mathrm{boundary
      faces}} B(b,C)
\end{equation}

@@

For RSOS realization of Ising model we have:
\begin{eqnarray}
  \label{eq:10}
  2 \cos\lambda = \sqrt{2}\\
  \lambda=\frac{\pi}{4}\\
  \psi = (1,\sqrt{2},1)
\end{eqnarray}
So we obtain Boltzmann weights:
\begin{equation}
  \label{eq:9}
  \begin{array}{l}
  W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) = \frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
  W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 3
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
  W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}}\frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
\end{array}
\end{equation}

>>>>

The weight of the spin configuration $C$ is equal to the product of
face weights and boundary weights:
\begin{equation}
  \label{eq:7}
  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mbox{\small{boundary
      faces}}} B(b,C)
\end{equation}

\subsection{Mapping of RSOS and tricritical model}
\label{sec:mapp-rsos-tricr}

Weights for $A_4$ RSOS model are:

@@

For RSOS realization of Ising model we have:
\begin{eqnarray}
  \label{eq:10}
  2 \cos\lambda = \sqrt{2}\\
  \lambda=\frac{\pi}{4}\\
  \psi = (1,\sqrt{2},1)
\end{eqnarray}
Values on even sublattice sites are fixed to $2$ and odd sublattice
values $1,3$ can be mapped to Ising spins $-1,+1$. Critical value for
Ising model is $K_C=\frac{1}{2}\log (1+\sqrt{2})$.

So we obtain Boltzmann weights:
\begin{equation}
  \label{eq:9}
  \begin{array}{lllll}
    V_{-} &=& W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) &=&   W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
H_{-}&=&W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 3
    \end{array}\right| u\right) &=&  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\

V_{+}&=&W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      1 & 2
    \end{array}\right| u
\right)&=&   W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      3 & 2
    \end{array}\right| u
\right)= \frac{\sin\left( u\right) }{\sqrt{2}\,\sin\left(
    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
    l\right) } = \sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
H_{+}&=&W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 1
    \end{array}\right| u
\right)&=&   W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 3
    \end{array}\right| u
\right)= \frac{\sqrt{2}\sin\left( u\right) }{\sin\left(
    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
    l\right) } = 2\sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)
\end{array}
\end{equation}
Here we have denoted by $V_{\pm}, H_{\pm}$ Boltzmann weights for
vertical and horizontal adjacent spins with positive ($+$) or negative
($-$) product. The case $u=\lambda/2=\frac{\pi}{8}$ is isotropic
$\frac{V_+}{V_-}=\frac{H_+}{H_-}= 1+\sqrt{2}=e^{2 K_C}$.

The crucial object in the proof of convergence of lattice correlations
to correlation functions in critical limit is parafermionic observable
of Smirnov, Hongler \cite{1202.2838v2}.

It can be defined as follows: consider Ising configuration on a double cover of domain $\Omega$
with singularity at $z$.
